Binary companions of red clump stars

### 2017-07-29 paper/main.tex
outline text

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Simple Monte Carlo gets a capital S to indicate that it is a defined thing.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Always prior pdf or posterior pdf, never prior or posterior (that's your arse).
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.

@@

@@

\begin{abstract}
% Context
Radial-velocity measurements can be used to find stellar, sub-stellar,
and planetary companions of stars.
In the \apogee\ survey, we have multi-epoch radial-velocity measurements
for many red-giant stars, including many red-clump (\RC) stars.
Spectral analysis of \RC\ stars can be used to deliver masses (with
XXX precision) and 20-ish chemical abundance measurements (with YYY
precision).
% Aims
Here we perform a search for secondary companions of [number] \RC\ stars.
Because the primary-star masses are known, the mass-function degeneracy
is broken and the secondary-companion $m\,\sin i$ values can be inferred.
Also, if the primary and companion are assumed to be co-eval, the
abundances of the \RC\ star can be assumed to represent accurately the
abundances of the secondary.
% Methods
We use a data-driven model (\thecannon) of stellar spectra to deliver
each \RC\ mass and chemical abundances, and a custom-built Monte Carlo
sampler (\thejoker) to deliver (often highly multi-modal) posterior
beliefs about companion $m\,\sin i$, period, and other orbital parameters.
Our sampler permits us to accurately sample even the badly behaved
posterior pdfs obtained when there are as few an NNN observation
epochs per star.
We put these posterior samples---made under an interim prior---into a
hierarchical inference to obtain individual-companion-marginalized
posterior beliefs about the properties of the full secondary-companion
distribution in mass and period.
In this analysis, even stars with only a few observations (and therefore
badly multimodal posterior pdfs) contribute valuable information to the
population inference.
% Results
We deliver a catalog of QQQ companions [that meet some criteria], and
posterior samplings for all [number] stars in the parent sample.
We find that the period and mass distributions [have some properties].
We look for trends with chemical abundances, and we find tentative evidence
for ZZZ and WWW.
\end{abstract}

@@

If we want to use a spectroscopic survey to responsibly measure the
binary-star population---that is, if we want to get (say) the mass,
mass ratio, and period distribution of binary star systems---we face
(at least) two challenges.
The first is how, given a small number of observations of a primary
star (a single-lined spectroscopic binary star), do we reliably obtain posterior
information about the binary-system properties?
After all, if there are only a few radial-velocity measurements made
per star, any observed radial-velocity values will be consistent with
many different combinations of period and amplitude (not to mention
eccentricity and argument of perihelion) for the primary orbit.
In general, the likelihood function, and the posterior pdf under any
reasonable prior pdf, will be highly multimodal in these kinds of
problems, and many of the modes will have comparable integrated
probability density.
We have solved this problem previously, though with limitations (to be
discussed more below), with \thejoker\ (CITE).
\thejoker\ is a Simple Monte Carlo rejection sampler that is
computationally expensive but probabilistically righteous: It delivers
independent (zero-auto-correlations) posterior pdf samples for
single-companion binary model parameters, given any number of
radial-velocity measurements.

@@

HOGG: What is up with delivering a catalog (it requires decision-making).

\section{Method: Detection and orbit fitting}

@@

\section{Method: Population inferences}

>>>>

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Simple Monte Carlo gets a capital S to indicate that it is a defined thing.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Always prior pdf or posterior pdf, never prior or posterior (that's your arse).
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.
% - Hyphenate binary-star when it is an adjective, not when it is a noun!

@@

% adjust ASS-TEX shit
\setlength{\parindent}{1.\baselineskip}

@@

\begin{abstract}\noindent % trust me
% Context
Radial-velocity measurements can be used to find stellar, sub-stellar,
and planetary companions of stars.
In the \apogee\ survey, we have multi-epoch radial-velocity measurements
for many red-giant stars, including many red-clump (\RC) stars.
Spectral analysis of \RC\ stars can be used to deliver masses (with
XXX precision) and 20-ish chemical abundance measurements (with YYY
precision).
% Aims
Here we perform a search for secondary companions of [number] \RC\ stars.
Because the primary-star masses are known, the mass-function degeneracy
is broken and the secondary-companion $m\,\sin i$ values can be inferred.
Also, if the primary and companion are assumed to be co-eval, the
abundances of the \RC\ star can be assumed to represent accurately the
abundances of the secondary.
% Methods
We use a data-driven model (\thecannon) of stellar spectra to deliver
each \RC\ mass and chemical abundances, and a custom-built Monte Carlo
sampler (\thejoker) to deliver (often highly multi-modal) posterior
beliefs about companion $m\,\sin i$, period, and other orbital parameters.
Our sampler permits us to accurately sample even the badly behaved
posterior pdfs obtained when there are as few an NNN observation
epochs per star.
We put these posterior samples---made under an interim prior---into a
hierarchical inference to obtain individual-companion-marginalized
posterior beliefs about the properties of the full secondary-companion
distribution in mass and period.
In this analysis, even stars with only a few observations (and therefore
badly multimodal posterior pdfs) contribute valuable information to the
population inference.
% Results
We deliver a catalog of QQQ companions [that meet some criteria], and
posterior samplings for all [number] stars in the parent sample.
We find that the period and mass distributions [have some properties].
We look for trends with chemical abundances, and we find tentative evidence
for ZZZ and WWW.
\end{abstract}

@@

If we want to use a spectroscopic survey to responsibly measure the
binary-star population---that is, if we want to get (say) the mass,
mass ratio, and period distribution of binary-star systems---we face
(at least) two challenges.
The first is how, given a small number of observations of a primary
star (a single-lined spectroscopic binary star), do we reliably obtain posterior
information about the binary-system properties?
After all, if there are only a few radial-velocity measurements made
per star, any observed radial-velocity values will be consistent with
many different combinations of period and amplitude (not to mention
eccentricity and argument of perihelion) for the primary orbit.
In general, the likelihood function, and the posterior pdf under any
reasonable prior pdf, will be highly multimodal in these kinds of
problems, and many of the modes will have comparable integrated
probability density.
We have solved this problem previously, though with limitations (to be
discussed more below), with \thejoker\ (CITE).
\thejoker\ is a Simple Monte Carlo rejection sampler that is
computationally expensive but probabilistically righteous: It delivers
independent (zero-auto-correlations) posterior pdf samples for
single-companion binary model parameters, given any number of
radial-velocity measurements.

@@

HOGG: What is up with delivering a catalog (it requires decision-making)?

\section{Data}

Overview of what \apogee\ is, and what data we are using.

How we updated the individual-visit radial velocity measurements.

What we did (if anything) with the missing visits.

\section{Method: Detection and orbit fitting}\label{sec:fitting}

APW: Should we start this section with a set of named assumptions, as we
did in Anderson et al?

Summary of \thejoker\ and what it does.

Any modifications or knob-settings for \thejoker?

@@

\section{Method: Population inferences}\label{sec:popinference}

Now we want to take the individual-star fits---or samplings---that
we made in \sectionname~\ref{sec:fitting} and, from these, produce
an inference of the properties of the whole \RC\ binary-star population.
Important necessary properties of this inference are the following:
\begin{description}
\item[foo] whatevs
\item[bar] and other
\end{description}
We can meet these requirements with a hierarchical Bayesian inference
(hierarchical probablistic model) of the binary-star population.

In addition to the above requirements, we make the following assumptions
that restrict our attention to a well-defined model space:
\begin{description}
\item[foo] whatevs
\item[bar] and other
\end{description}

The binary-system parameters for each individual \RC\ star were
inferred (in \sectionname~\ref{sec:fitting}) with an interim prior that
is very simple and doesn't represent our true beliefs about the
binary-star population...

In a hierarchical Bayesian inference, we replace the binary-star
system priors used in \sectionname~\ref{sec:fitting} with a parameterized
model for the binary-star population...

Because all we have is a sampling of each system under the interim prior,
we have to re-weight or importance-sample the individual-star samplings
in this hierarchical inference... Cite Hogg et al; Cite DFM et al.
